### 2017-11-13 README.Rmd
travis updates

[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/WetlandComparison.svg?branch=master)](https://travis-ci.org/samdchamberlain/WetlandComparison)

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("samdchamberlain/WetlandComparison")
```

>>>>

[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/wetlandcomparison.svg?branch=master)](https://travis-ci.org/samdchamberlain/wetlandcomparison)

@@

```{r gh-installation, eval = FALSE}
install.packages("devtools")
devtools::install_github("samdchamberlain/WetlandComparison")
```
